QPLIB: A Library of Quadratic Programming Instances

### 2017-02-02 format.tex
binary variables now always have lower bound 0 and upper bound 1
- thus, no bounds can be specified for binary variables
- thus, bounds sections can be ignored for *B* type instances
- see discussion in d4e031c1

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. In case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*} and for variables that are specified explicitly as binary variables, the default values for lower and upper bounds of a binary variables are assumed to be 0 and 1, respectively, independent of the specification of $l_d$ and $u_d$.
%Note, that in case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\end{description}

>>>>

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. In case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*}, this section is omitted.
Bounds for binary variables must not be specified in this section. They are assumed to have a lower bound of 0 and an upper bound of 1, disregarding any setting of $l_d$ and $u_d$. To fix a binary variable to 0 or 1, either a corresponding linear equation must be added or the variable type should be changed to continuous or general integer.
\end{description}
